---
title: "pnadc_tracks"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pnadc_tracks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(PNADc.table)
library(PNADcIBGE)
library(webshot2)
```

# What is it for?
<div style="text-align: justify">
The _pnadc_tracks_ function is used to create **tables with grouping tracks** and export them in csv (Excel), html, pdf formats and also create a Data Frame in R environment.

# arguments
<div style="text-align: justify">
* **Variable**:
Feature of interest that will be used for calculations. It must be a numeric variable and be written as a formula (~ in front of the variable). Non-numeric/empty remarks are disregarded.

* **Filter**:
Variable that defines the aggregation level of the variable of interest. It can contain more than one level of aggregation. It also needs to be written as a formula.

* **Year**:
Year you want to analyze. Must be a number between 2012 and the current year. Does not accept a vector of years. If the chosen edition has not yet been downloaded, the _pnadc_download_ function will be called automatically and create a design in the desired location.

* **Quartile**:
Quartile of the year you want to analyze. Must be a number between 1 and 4. It does not accept a vector of quartiles.

* **Calculation**:
calculation you want to do. Must be one of: mean, total and percentage. It must come between "". It does not accept a list of calculations.

* **Group**:
Variable that will serve to group the data set. It wants to be one of the variables listed in the Filter. It must be a formula.

* **Cluster**:
How the grouping strip will be made. In the numerical case it must be a **vector** containing the minimum, maximum and size of the range you want to create. In the categorical case it must be a **list** containing the old names and the new name that will replace them.

* **Path**:
Location/directory where you want to save the final table. If you have already used the _pnadc_download_ function to create the design in a specific path, just use the logical value True (T). If a path is not chosen, the table will be saved in the user folder on the local hard disk.

* **Export**:
Format in which you want to export the generated table. It can export to "html", "pdf", "png", "csv" and "rtf". If you want to return a data frame in R space, use "df". If it has not been filled, it returns a gt_table in R space. It must be a string (come between " ").

# What does the function return?
<div style="text-align: justify">
The function returns a **gt table** within the R environment if the **export option is not filled**. If the export argument is filled with one of the other options, the function will create a file directly in the informed directory.

# Examples:
<div style="text-align: justify">
In this example we are going to create a table of the mean of the monthly gross income (V403312) separated by age group of 5 in 5 years of the PNADc of 2019.1 calculating that the user did not use the _pnadc_download_ function to download the files and also does not want to export the table .

```{r}
pnadc_tracks(~V403312, ~V2009, 2019, 1, calculation = "mean", group = ~V2009, cluster = c(0, 100, 5))
#The filter argument uses the Age variable (V2009).
#The selected calculation must be "mean" to generate the means table.
#The group will be the filter itself since we are working with only one filter.
#The cluster is a vector containing the minimum age, maximum age and size of the range we want to create.
#NOTE: As there are no observations in ages 0 to 10, the range is null and is not listed.
```

<div style="text-align: justify">
For cases where the filter has more than one variable, we would have the following example:
```{r}
pnadc_tracks(~V403312, ~V2009+UF, 2019, 1, calculation = "mean", group = ~V2009, cluster = c(0, 100, 5))
# We add UF to the filter
#The table generated will be the Gross Income (V403312) x UF x Age Group
```

<div style="text-align: justify">
Now we will create an example to group the Races (V2010) as follows: White = White, Black = Black and Brown and Others = Yellow, Indigenous and Ignored. Now the **cluster** will be a **list**

```{r}
pnadc_tracks(~V403312, ~V2010, 2019, 1, calculation = "mean", group = ~V2010, cluster = list("Negra" = c("Preta","Parda"), "Outras" = c("Amarela","Indígena","Ignorado")))
#Must make a list of vectors for the cluster argument.
#New names must come first and then the names you want to replace.
```

<div style="text-align: justify">
Let's redo the previous tables, but now with the **percentage**:

```{r}
pnadc_tracks(~V403312, ~V2009+UF, 2019, 1, calculation = "percentage", group = ~V2009, cluster = c(0, 100, 5))

pnadc_tracks(~V403312, ~V2010, 2019, 1, calculation = "percentage", group = ~V2010, cluster = list("Negra" = c("Preta","Parda"), "Outras" = c("Amarela","Indígena","Ignorado")))
```

<div style="text-align: justify">
Now let's **export** the previous tables to a pre-selected folder

```{r}
pnadc_tracks(~V403312, ~V2009+UF, 2019, 1, calculation = "percentage", path = "C:/Data_PNADc", group = ~V2009, cluster = c(0, 100, 5), export = "pdf" )
#As the path has been selected, the function will download and create the design directly in the chosen directory
#The export option chosen was in .pdf
#The table will be exported to the location C:\Data_PNADc in .pdf format

pnadc_tracks(~V403312, ~V2010, 2019, 1, calculation = "percentage", path = "C:/Data_PNADc", group = ~V2010, cluster = list("Negra" = c("Preta","Parda"), "Outras" = c("Amarela","Indígena","Ignorado")), export = "csv")
# The export option chosen was in .csv
#The table will be exported to the location C:\Data_PNADc in .csv format
```

<div style="text-align: justify">
If the objective is to create a **Data Frame in R**, the user must assign it to an object, that is, an object will be created in the R environment and it will receive the final result of the function.
<br/>Although it sounds strange, this task is actually quite simple. Let's take the previous example to create the Data Frame

```{r}
table_pnadc_2019_1 <- pnadc_tracks(~V403312, ~V2009+UF, 2019, 1, calculation = "percentage", path = "C:/PNADc_Data", group = ~V2009, cluster = c(0, 100, 5), export = "df")
#As "df" was selected in the "export" argument, the function will return a Data Frame.
#We assign to the object "table_pnadc_2019_1" the Data Frame of the function, in this way it will be saved so it can be used later. view(table_pnadc_2019_1)
```

<div style="text-align: justify">
Some general examples of how the function can be used:

```{r}
pnadc_tracks(~V403312, ~V2009+UF, 2019, 1, calculation = "total", group = ~V2009, cluster = c(0, 100, 5))
```

# NOTE:
Code execution will be faster or slower depending on the **processing speed** of the computer and the amount of **RAM** available.
